Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-06-13 analysis_parameters.tex
fixing figures

\begin{figure*} [!ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
\caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
\label{fig:completness_scatter}
\end{figure*}

@@

\begin{figure*} [!ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
\caption{Cumulative number of earthquakes with respect to the time. Magnitude range is represented in a box at the top left corner. Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period. Green dashed lines represents the completeness threshold reported by \citet{Zare2014}. Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
\label{fig:completness_compare_zare_2014_Az_Al}
\end{figure*}

@@

\begin{figure*} [!ht]
\centering
\includegraphics[scale=0.28]{figures/pdf/figure-07.pdf} 
\caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
\label{fig:comp_test_all_mag}
\end{figure*}

>>>>

% \begin{figure*} [!ht]
% \centering
% \includegraphics[scale=0.5]{figures/pdf/figure-05.pdf} 
% \caption{Magnitude-time distribution of earthquakes in the study regions. a) Alborz, b) Azerbaijan, c) Central, d) Kopeh Dagh, e) Uniform f) Zagros}
% \label{fig:completness_scatter}
% \end{figure*}

@@

% \begin{figure*} [!ht]
% \centering
% \includegraphics[scale=0.4]{figures/pdf/completness_compare_zare_2014_Az_Al.pdf} 
% \caption{Cumulative number of earthquakes with respect to the time. Magnitude range is represented in a box at the top left corner. Solid black lines represent the starting of early instrumental (1900) and instrumental (1961) period. Green dashed lines represents the completeness threshold reported by \citet{Zare2014}. Arrows show the possible places to choose as completeness threshold after \citet{Frankel1995}.}
% \label{fig:completness_compare_zare_2014_Az_Al}
% \end{figure*}

@@

% \begin{figure*} [!ht]
% \centering
% \includegraphics[scale=0.28]{figures/pdf/figure-05.pdf} 
% \caption{Magnitude-time distribution of earthquakes in the study regions. a-b) Alborz, c-d) Azerbaijan, e-f)Central, g-h)Kopeh Dagh, i-j)Zagros}
% \label{fig:comp_test_all_mag}
% \end{figure*}

### 2016-06-13 composition.tex
fixing figures

Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}. In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with all $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks. The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}.

>>>>

Selection and declustering was also done in consistence with the original catalog, using the method of \citet{Gardner1974}. In summary, we obtained the whole catalog version of \citet{Zare2014}, removed the events from 2000 and forward, complemented the catalog with all $M>3$ events up to 2015 from IIEES, and finally declustered the new complemented catalog removing foreshocks and aftershocks. The resulting set of events compiled for this study is shown in Fig.~\ref{fig:catalog}, which shows the spatial distribution within the region of interest for both historical and instrumental events. In turn, Fig.~\ref{fig:scatter} shows the distribution of events in time and magnitude for each of the seismic zones, as well as for the complete region of interest (here referred to as the uniform model).

\begin{figure*} [t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
	\label{fig:scatter}
\end{figure*}

### 2016-06-13 parameters.tex
fixing figures

\begin{table*}[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{lccc}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.10 $\pm$ 0.03   & 7.93 $\pm$ 0.34   & 7.7                       \\
        Alborz          & 1.03 $\pm$ 0.03   & 7.85 $\pm$ 0.66   & 7.8                       \\
        Kopeh Dagh      & 0.89 $\pm$ 0.04   & 7.78 $\pm$ 0.31   & 7.6                       \\
        Zagros          & 0.99 $\pm$ 0.02   & 7.47 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.95 $\pm$ 0.04   & 7.84 $\pm$ 0.34   & 7.6                       \\
        Uniform Model   & 0.90 $\pm$ 0.02   & 7.87 $\pm$ 0.26   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table*}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-04} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for seismic tectonic regions of (a) Alborz, (b) Azerbaijan, (c) Central Iran, (d) Kopeh Dagh, (e) Uniform (f) Zagros. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

>>>>

\begin{table}[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.10 $\pm$ 0.03   & 7.93 $\pm$ 0.34   & 7.7                       \\
        Alborz          & 1.03 $\pm$ 0.03   & 7.85 $\pm$ 0.66   & 7.8                       \\
        Kopeh Dagh      & 0.89 $\pm$ 0.04   & 7.78 $\pm$ 0.31   & 7.6                       \\
        Zagros          & 0.99 $\pm$ 0.02   & 7.47 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.95 $\pm$ 0.04   & 7.84 $\pm$ 0.34   & 7.6                       \\
        Uniform Model   & 0.90 $\pm$ 0.02   & 7.87 $\pm$ 0.26   & 7.8                       \\[0.5ex]
        \hline 
    \end{tabular}
    \label{tab:params} 
\end{table}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-06} 
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. THe last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}
